An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/intro.tex
better wording

In order to overcome these obstacles,
researchers have proposed 
statistical analysis and learning-based approaches%
~\cite{wang04automatic, zhang14encore, yuan11context}. 
These efforts build checking policies by learning a sample 
data set, rather than explicitly specifying entries' types or rules.
In particular, for each entry in a certain configuration file, 
if it deviates from the common values used in a large collection
of configurations (\ie, the data set for training), it is typically
suspected as a potential configuration error.
However, because these learning 
efforts {\em either} are limited to simplistic 
configuration errors (\eg, type errors and syntax errors), 
{\em or} heavily rely on template-based inference~\cite{zhang14encore}, 
many sophisticated configuration errors, 
\eg, hard to be templated in practice, cannot be detected.
For example, if {\tt extension = mysql.so} appears 
before {\tt extension = recode.so} in PHP configuration file,  
it would lead to a crash error, since the correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical};
however, such an error cannot be detected by existing
learning efforts, since it is hard to build a template for this
error~\cite{xu15systems}.

>>>>

In order to overcome these obstacles,
researchers have proposed 
statistical analysis and learning-based approaches%
~\cite{wang04automatic, zhang14encore, yuan11context}. 
These efforts build checking policies by learning from a sample 
data set, rather than explicitly specifying entries' types or rules.
In particular, for each entry in a certain configuration file, 
if it deviates from common values used in a large collection
of configuration files (\ie, the data set for training), it is typically
suspected to contain a potential configuration error.
However, because these learning 
efforts {\em either} are limited to simplistic 
configuration errors (\eg, type errors and syntax errors)
{\em or} heavily rely on template-based inference~\cite{zhang14encore}, 
many sophisticated configuration errors, 
which are difficult to template in practice, cannot be detected.
For example, if {\tt extension = mysql.so} appears 
before {\tt extension = recode.so} in a PHP configuration file,  
it would lead to a crash error, since the correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical};
however, such an error cannot be detected by existing
learning efforts, since it is hard to build a corresponding template ~\cite{xu15systems}.
